Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-06-28 ms.tex
Added several fixes to intro, explained reference time and changed the symbol for flux from I to F.

\begin{figure*}
\centering
	\plottwo{image0835-0819.pdf}{image1821+1414.pdf}
	\label{fig:image1821}
	\vspace{-.9in}
	\caption{2MASS $JHK_s$ three-color images of the fields around our targets {\sha} (left) and {\shb} (right)
	from the IRSA Finderchart service (\url{http://irsa.ipac.caltech.edu/applications/finderchart/}).  Each image is centered on the target, and span a 1$\arcmin\times\arcmin$ field of view oriented with North up and East the left. The comparison stars referred to in the text appear as blue sources in these images. }
	\label{fig:images}
	\vspace{0.17in}
\end{figure*}

This article reports the results of a pilot study adapting these methods to measuring the variability of two L-type dwarfs with nearby visual companions. We describe our target selection process and pilot target properties in Section~\ref{sec:targets}.
In Section~\ref{sec:obs}, we describe our monitoring observations and data reduction procedures to generate relative spectro-photometric time series.
In Section~\ref{sec:analysis}, we analyze these time series using sinusoidal model fits over discrete spectral bands to generate individual light curves and amplitude spectra.
We then fit the variability amplitude spectra to two different physical models, Mie scattering from clouds and heterogeneous temperature spots, to assess which more accurately reproduces the data.
We summarize our results in Section~\ref{sec:conclusions}.

@@

We computed brightness temperature spectra from these data as
\begin{equation}
T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{I_{\lambda,surf}\lambda^5}\right)\right]^{-1}
\end{equation}
where the surface flux density $I_{\lambda,surf}$ is computed as
\begin{equation}
I_{\lambda,surf} = {\pi}B_{\lambda} = I_{\lambda,obs}\left(\frac{d}{R}\right)^2 = I_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2
\end{equation}
$I_{\lambda,obs}$ and $I_{\lambda,abs}$ are the observed and absolute flux densities, $d$ the source distance and $R$ the source radius.  Both spectra were calibrated to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes \citep{2016MNRAS.455..357S,2016AJ....152...24W}. We adopted radii from the evolutionary models of \citet{2003A&A...402..701B} assuming bolometric luminosities from \citet{2015ApJ...810..158F} for {\sha} and from\footnote{The parameters reported for {\shb} in \citet{2016ApJS..225...10F} are in error, but have been updated here based on a forthcoming erratum (J.\ Faherty, 2017, priv.\ comm.).}  \citet{2016ApJS..225...10F} for {\shb} (Table~\ref{tab:bdProp}). Uncertainties in the spectral fluxes, absolute photometric calibration, adopted {\lbol} and radius were propagated by Monte Carlo simulation.  For {\sha} we considered two cases: radii of 0.114--0.137~R$_{\odot}$ for ages of 50--200~Myr, the age range estimated for INT-G sources by \citet{2013ApJ...772...79A}; and radii of 0.088--0.101~R$_{\odot}$ for ages of 0.5--3~Gyr; i.e., a field dwarf age.
For {\shb}, we assumed an lower age limit of 200~Myr based on its field gravity classification, and an upper limit of 700~Myr based on the analysis of \citet{2016MNRAS.455..357S}. The Baraffe et al.\ evolutionary models predict radii of 0.097--0.114~R$_{\odot}$ for these ages and the luminosity of {\shb}.

@@

As seen in Figure~\ref{fig:tserDetrend}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particularly in bands $<$1.8~$\mu$m. 
These variations are periodic with ``double-hump'' structures at peak amplitudes around -2.7~hr and +1.3~hr. {\bf [relative to what time?]}
The amplitude of these variations is strongly wavelength-dependent with $\sim$3.0\% peak-to-trough variations at short 
wavelengths and near-zero amplitude at the longest wavelengths.
A possible difference between the two brown dwarfs is the viewing geometry with \sha\ closer to pole-on and \shb\ closer to equator-on as shown in Table \ref{tab:bdProp}.
Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.

>>>>

\begin{figure*}
\centering
	\plottwo{image0835-0819.pdf}{image1821+1414.pdf}
	\label{fig:image1821}
	\vspace{-.9in}
	\caption{2MASS $JHK_s$ three-color images of the fields around our targets {\sha} (left) and {\shb} (right)
	from the IRSA Finderchart service (\url{http://irsa.ipac.caltech.edu/applications/finderchart/}).  Each image is centered on the target, and span a 1$\arcmin\times\arcmin$ field of view oriented with North up and East the left. The comparison stars referred to in the text appear as blue sources in these images.
	For \sha\, we use the comparison star to the left and for \shb\ the lower right.}
	\label{fig:images}
	\vspace{0.17in}
\end{figure*}

This article reports the results of a pilot study adapting these methods to measuring the variability of two L-type dwarfs with nearby visual companions. We describe our target selection process and pilot target properties in Section~\ref{sec:targets}.
In Section~\ref{sec:obs}, we describe our monitoring observations and data reduction procedures to generate relative spectro-photometric time series.
In Section~\ref{sec:analysis}, we analyze these time series using sinusoidal model fits over discrete spectral bands to generate individual light curves and amplitude spectra.
We then fit the variability amplitude spectra with a Mie extinction model for the clouds and constrain the particle size distribution.
We summarize our results in Section~\ref{sec:conclusions}.

@@

We computed brightness temperature spectra from these data as
\begin{equation}
T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{F_{\lambda,surf}\lambda^5}\right)\right]^{-1}
\end{equation}
where the surface flux density $F_{\lambda,surf}$ is computed as
\begin{equation}
F_{\lambda,surf} = {\pi}B_{\lambda} = F_{\lambda,obs}\left(\frac{d}{R}\right)^2 = F_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2
\end{equation}
$F_{\lambda,obs}$ and $F_{\lambda,abs}$ are the observed and absolute flux densities, $B_\lambda$ is the Planck function, $d$ the source distance and $R$ the source radius.  Both spectra were calibrated to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes \citep{2016MNRAS.455..357S,2016AJ....152...24W}. We adopted radii from the evolutionary models of \citet{2003A&A...402..701B} assuming bolometric luminosities from \citet{2015ApJ...810..158F} for {\sha} and from\footnote{The parameters reported for {\shb} in \citet{2016ApJS..225...10F} are in error, but have been updated here based on a forthcoming erratum (J.\ Faherty, 2017, priv.\ comm.).}  \citet{2016ApJS..225...10F} for {\shb} (Table~\ref{tab:bdProp}). Uncertainties in the spectral fluxes, absolute photometric calibration, adopted {\lbol} and radius were propagated by Monte Carlo simulation.  For {\sha} we considered two cases: radii of 0.114--0.137~R$_{\odot}$ for ages of 50--200~Myr, the age range estimated for INT-G sources by \citet{2013ApJ...772...79A}; and radii of 0.088--0.101~R$_{\odot}$ for ages of 0.5--3~Gyr; i.e., a field dwarf age.
For {\shb}, we assumed an lower age limit of 200~Myr based on its field gravity classification, and an upper limit of 700~Myr based on the analysis of \citet{2016MNRAS.455..357S}. The Baraffe et al.\ evolutionary models predict radii of 0.097--0.114~R$_{\odot}$ for these ages and the luminosity of {\shb}.

@@

As seen in Figure~\ref{fig:tserDetrend}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particularly in bands $<$1.8~$\mu$m. 
These variations are periodic with ``double-hump'' structures at peak amplitudes around -2.7~hr and +1.3~hr relative to JD 2457565.00.
The amplitude of these variations is strongly wavelength-dependent with $\sim$3.0\% peak-to-trough variations at short 
wavelengths and near-zero amplitude at the longest wavelengths.
A possible difference between the two brown dwarfs is the viewing geometry with \sha\ closer to pole-on and \shb\ closer to equator-on as shown in Table \ref{tab:bdProp}.
Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.
